\bf The Left Arm Bias in ITF Taekwon-Do Patterns \\ Chon-Ji to Juche

### 2010-07-16 article.tex
Completed section on Tags, plus minor refactoring

  % see the article: The Structure of Collaborative Tagging Systems
  % located in ~/tmp/tags.pdf

@@

\SubSection{Tags and Tagging}

%   Applying tags (to dataset)
%   Tagging
%     Group of tags
%     Groups of techniques {blocks, strikes, thrusts, punches}
%       height
%       weapon
%       type etc.

@@

  all articles on birds
  all articles on africa
  all articles on african birds
  all articles on birds from africa

@@

% go through different folder setup
% then insert the text about ``Tags, on the other hand..''
% elaborate what it means that an object can have many tags
% show a venn diagram
% explain the venn diagram

\def\A{A}
\def\B{\V{B}}

@@

  Tags, on the other hand, are \emph{non-hierarchical} and \emph{inclusive},
  which is to say that an object can be associated with a great variety of
  tags simultaneously\cite{golder:ct}.

  % Finally we can define tags as being non-hierarchical..
  \emph{Tags} are non-hierarchical descriptive terms, keywords or labels that
  is attached to an object for later
  retrieval\cite{golder:ct}\cite{huang:tt}\cite{shirky:ontology}\cite{wikipedia:tags}.

  %(mention polyhierarchical from the IA book)

  %Descriptive terms, keywords or labels are metadata associated with a given
  %object used to describe a concept or type of information\cite{heymann:ccch}.

  %Object.. (define an object, then say that in this article an object is a
  %pattern movement || a movement in a pattern)

  %Later retrieval..

% what does this all mean?
%   non-hierarchical
%   descriptive terms, keywords or labels
%   object (a movement in a pattern)

% Why do we tag?
%   this kind of metadata helps describe an item
%   allows it to be found again by searching
%   future navigation, filtering or search
%   later retrieval
%   categorize content using keywords
%   grouping related objects
%   classifies
%   organize
%   for the purpose of classification and retrieval
% How do we tag (tagging)?
%   define tagging

%\emph{Tagging} can be defined as the practice of creating and managing labels
%that categorize content using simple keywords

Tagging is the act of organizing a collection of entities, whether things or
concepts, into related groups\cite{shirky:ontology}.

@@

@@

>>>>

@@

\SubSection{Tags}

@@

@@

  The directory structure of (1), and (2) make central the fact that the
  folders are about ``birds'' and ``africa''. But, they don't tell anything
  about the other category. In (3) and (4) the files are organized by both
  categories, and show that there is a parent-child or sibling relationships
  between the folder names\cite{mathes:folk}.

  \emph{Tags}, on the other hand, are non-hierarchical descriptive terms,
  keywords or labels that is attached to an object for later retrieval
  \cite{golder:ct}\cite{huang:tt}\cite{shirky:ontology}\cite{wikipedia:tags}.

  They are \emph{non-hierarchical} and \emph{inclusive}, which is to say that
  an object can be associated with a great variety of tags
  simultaneously\cite{golder:ct}. The \emph{descriptive terms},
  \emph{keywords} or \emph{labels} are metadata connected to a given object
  which describe a concept or type of information\cite{heymann:ccch}.

\SubSection{Tagging}

  Tagging is the act of organizing a collection of objects into related
  groups\cite{shirky:ontology}.

% Why do we tag?
%   this kind of metadata helps describe an item
%   allows it to be found again by searching
%   future navigation, filtering or search
%   later retrieval
%   categorize content using keywords
%   grouping related objects
%   classifies
%   organize
%   for the purpose of classification and retrieval
%   display venn diagram
%   explain venn diagram
% How do we tag (tagging)?
%   define tagging

% end the section with something like..
% tags add metadata to an object
% tagging groups objects
% the reason for why we bother is because we want to find the objects again

\SubSection{Retrieval}

% explain how later retrieval is done by using the venn diagram

% Venn diagram
\def\A{A}
\def\B{\V{B}}

@@

@@

%   Tagging
%     Group of tags
%     Groups of techniques {blocks, strikes, thrusts, punches}
%       height
%       weapon
%       type etc.

@@

    \bibitem{mathes:folk}
      Adam Mathes,
      ``Folksonomies -- Cooperative Classification and Communication Through
      Shared Metadata,''
      \emph{Computer Mediated Communication, LIS590CMC}, 2004.
